---
title: "Isochrone"
author: "Leonard-Allen"
Last Update: 7/05/2022
output:
  html_document:
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: yes
    theme: readable
  pdf_document:
    toc: yes
    toc_depth: '4'
colorlinks: yes
urlcolor: blue
linkcolor: blue
citecolor: blue
anchorcolor: blue
toccolor: blue
fontsize: 12pt
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Loading my packages

```{r}
#setwd("C:/Users/Leo Allen/Desktop/Isochrones/isochrones")  #set the working directory

library(RColorBrewer)
library(traveltime)
library(tidyverse)
library(tidycensus)
library(sf)
library(osmdata)
library(leaflet)
library(sp)
library(purrr)
library(mapview)
library(osrm)
library(rmapzen)
library(rgdal)
library(ggplot2)
library(scales)
library(nycflights13)
library(readxl)
library(rgdal)
```

#TRAVELTIME; install this in R console (NOT R STUDIO)!!!
#Install the latest version of this package by entering the following in R:
#install.packages("remotes")
#remotes::install_github("tlorusso/traveltimeR")

```{r}
#install.packages("remotes")
#remotes::install_github("tlorusso/traveltimeR")
```



#getting population and maps of surrounding of page from acs
#I registered for my personal key from the website

##############
#travel time, I did this once to generate center RDS file
#to get the api and the id I visited the website and signed up:
#https://traveltime.com/docs/api/overview/getting-keys

```{r}

YourAPIKey <- "eb02516c05b7d10f8e03477312b537fa"
YourAppId <- "acfb52eb"

```

# Checks: latitude, Longitude, seconds
# Also, departure time must lie in the future.

```{r}
# retrieve data via request 

# The following transport modes are supported:

# "cycling"", "cycling_ferry", "driving", "driving+train", "driving_ferry", "public_transport", 
# "walking", "walking+coach", "walking_bus", "walking_ferry" or "walking_train".

# how far can you go by public transport within 30 minutes?

# Travel times for 2021
traveltime15 <- traveltime_map(appId=YourAppId,
              apiKey=YourAPIKey,
              location=c(37.534379575044426,-77.44071077873014),
              traveltime=900,
              type="driving",
              departure="2021-07-07T08:00:00+01:00") %>%
  st_set_crs(st_crs("EPSG:4326"))
traveltime30 <- traveltime_map(appId=YourAppId,
              apiKey=YourAPIKey,
              location=c(37.534379575044426,-77.44071077873014),
              traveltime=1800,
              type="driving",
              departure="2021-07-07T08:00:00+01:00") %>%
  st_set_crs(st_crs("EPSG:4326"))
traveltime45 <- traveltime_map(appId=YourAppId,
              apiKey=YourAPIKey,
              location=c(37.534379575044426,-77.44071077873014),
              traveltime=2700,
              type="driving",
              departure="2021-07-07T08:00:00+01:00") %>%
  st_set_crs(st_crs("EPSG:4326"))
traveltime60 <- traveltime_map(appId=YourAppId,
              apiKey=YourAPIKey,
              location=c(37.534379575044426,-77.44071077873014),
              traveltime=3600,
              type="driving",
              departure="2021-07-07T08:00:00+01:00") %>%
  st_set_crs(st_crs("EPSG:4326"))
```

```{r eval=FALSE, include=FALSE}
# Importing the data with centroid coordinates
aoi_boundary_POW <- st_read("Powhatan_Parcel_Data/Powhatan_Travel_Time/Powhatan_Travel_Times.shp") %>% st_transform(crs = st_crs("EPSG:4326"))
aoi_boundary_POW$Trv2RcMnd <- factor(aoi_boundary_POW$Trv2RcMnd, levels = c("30 minutes", "45 minutes", "One hour", "More than an hour"))
# Custom color palette
mypalette <- colorBin(palette = "viridis", as.numeric(aoi_boundary_POW$Trv2RcMnd), bins = 5)
colors <- mypalette(unclass(aoi_boundary_POW$Trv2RcMnd))
sorted_colors <- c("#440154", "#2A788E", "#7AD151", "#FDE725")

#aoi_boundary_POW30 <- aoi_boundary_POW %>% filter(Trv2RcMnd == "45 minutes")


# First provider shape file of the county boundary, so first addPolygons

map <-leaflet() %>%
  addTiles() %>%
  addProviderTiles("Esri") %>%  
  
  # powhatan parcels colored by distance
  addPolygons(data=aoi_boundary_POW$geometry, color = "black",
              fillColor = colors,
              smoothFactor = 0.1, fillOpacity=.6, weight = 1,stroke = T, ) %>%
  
  # driving times from richmond
  addPolygons(data = traveltime30, color = "Yellow",
               opacity = 1, weight = 2, fillColor = "white",fillOpacity = .1, 
              group = "Within 30") %>%
  addPolygons(data = traveltime45, color = "Orange",
               opacity = 1, weight = 2, fillColor = "white",fillOpacity = .1,
              group = "Within 45") %>%
  addPolygons(data = traveltime60, color = "Red",
               opacity = 1, weight = 2, fillColor = "white",fillOpacity = .1,
              group = "Within 60") %>%
  addCircleMarkers(lat = 37.534379575044426, lng = -77.44071077873014, label = "Richmond") %>%
  addLegend("bottomright", 
            colors= sorted_colors,
            labels = traveltime_categories,
            title = "Travel Times in Minutes (2021)", 
            opacity = 1) %>%
  addLayersControl(
    baseGroups=c("Within 30", "Within 45", "Within 60"),
    position = "bottomleft",
    options = layersControlOptions(collapsed = FALSE)
  )
  
map
```

```{r}
# st_write(traveltime30, "30MinuteTravelTime.shp")
# st_write(traveltime45, "45MinuteTravelTime.shp")
# st_write(traveltime60, "60MinuteTravelTime.shp")
```




# Useful link

[Website](https://tlorusso.github.io/traveltime/vignette.html#:~:text=traveltime%20%2D%20a%20Traveltime%20API%20Wrapper%20for%20R,-1%20Querying%20the&text=The%20isochrones%20display%20how%20far,modes%20of%20transport%20are%20supported.&text=For%20non%2Dcommercial%20use%20the,max%2030%20queries%20per%20min)